---
title: "Survival"
author: "Achintya Varma"
date: "6/1/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
All the functions used in the analysis are defined below in the first chunk:
```{r}
suppressMessages(require(survival))
suppressMessages(require(survminer))
suppressMessages(require(dplyr))
suppressMessages(require(permute))
suppressMessages(require(gridExtra))
suppressMessages(require(ggplot2))
  
cox_asummption_check<-function(x){
  surv_obj<- Surv(time = x$date_diff, event = x$censoring)
return(list(cox.zph(res_cox),res_cox))
}

regression_output<-function(x){s<-summary(x)$conf.int
                              s1<-summary(x)$coefficients
                              return(cbind(as.data.frame(s),as.data.frame(s1)))
                              }

```

Following Code uses the data processing step for the survival analysis part of the analysis and creates the survival objects needed for the analysis of the project

```{r DataProcessing-Survival_Outcomes}
require(survminer)
require(survival)

HNDCleanSurv<-HNDCleanSurvival
HNDCleanSurv$dss_cens<-ifelse(HNDCleanSurv$dss=="Alive or did not die from HN cancer",0,1)
#table(HNDCleanSurvival$dss_cens,HNDCleanSurvival$dss)
HNDCleanSurv$LivingC<-ifelse(HNDCleanSurv$Living=="Yes (alive)",0,1)
#table(HNDCleanSurvival$LivingC,HNDCleanSurvival$Living)
HNDCleanSurv$LCRC<-ifelse(HNDCleanSurv$LCR=="Yes",0,1)
#table(HNDCleanSurvival$LCRC,HNDCleanSurvival$LCR)
censored_events<-as.data.frame(cbind(HNDCleanSurv$`Record ID`,HNDCleanSurv$dss_cens,HNDCleanSurv$LivingC,HNDCleanSurv$LCRC))

colnames(censored_events)<-c("rec_id",colnames(HNDCleanSurv[,9:11]))

SurvivalHND_sites<-as.data.frame(SurvivalHND_Sites)
HNDCleanSurv<-HNDCleanSurv[HNDCleanSurv$`Record ID` %in% SurvivalHND_stage$record_id,]

HNDCleanSurvivalD<-apply(HNDCleanSurv[,6:8],2,function(x){as.Date(x,format="%m/%d/%Y")})
dates_list<-colnames(HNDCleanSurvivalD)

HNDCleanSurvivalD<-apply(HNDCleanSurv[,5:8],2,function(x){as.Date.POSIXct(x,tz="America/New_York",format = "%m/%d/%Y")})

date_diff<-apply(HNDCleanSurvivalD[,2:4],2,function(x){x -HNDCleanSurvivalD[,1] })
date_diff<-date_diff/365
date_diff<-as.data.frame(cbind(HNDCleanSurv$`Record ID`,date_diff))
colnames(date_diff)<-c("rec_id",colnames(date_diff[,2:4]))

survival_master<-inner_join(date_diff,censored_events,by="rec_id")
#survival_master<-survival_master[,c(1,2,3,4,7,6,5)]

```
The following chunk creates the covariates for the survival analysis.
```{r Data Processing- Covariates}

Cov_Surv<-as.data.frame(cbind(SurvivalHND$`Record ID`,SurvivalHND$`Treatment interrupted`,SurvivalHND$`Site Multiple Choice-Drop Down (only one choice)`,SurvivalHND$`Stage for Cox Regression`,SurvivalHND$`ECOG for Cox Regression`,SurvivalHND$`Age for cox`,SurvivalHND$`CCI for Cox Regression`))

colnames(Cov_Surv)<-c("rec_id","trt","Site","stage","ecog","age","CCI")

Cov_Surv<-Cov_Surv[Cov_Surv$rec_id %in% survival_master$rec_id,]

```
The following chunk is needed for the creation of the objects needed for survival analysis. Function "reg_output" prints out the desired format we need for the project to print it in .csv file. 

```{r Creation of Objects}
#survival_master<-survival_master[survival_master$rec_id %in% SurvivalHND_Sites$record_id,]
surv_objs<-mapply(FUN=surv_obj_repeat,x=survival_master[,2:4],y=survival_master[,5:7])
names
 # Function creates survival objects with censoring)})
Cov_Surv<-Cov_Surv[Cov_Surv$rec_id %in% survival_master$rec_id,]
suv_fits<-lapply(surv_objs,function(y){lapply(Cov_Surv[,2:ncol(Cov_Surv)],function(x){surv_fit(y~x,data=Cov_Surv)})})
Cov_Surv$Site<-relevel(Cov_Surv$Site,ref="Oropharynx")

reg_output_l<-lapply(Cov_Surv[,2:7],function(x){regression_output(coxph(surv_objs$DC~x))}) # prepares all the outputs for DC for univariate 
survival_master2<-survival_master[survival_master$rec_id %in% data_mv$record_id,]
surv_objs2<-mapply(FUN=function(x,y){return(Surv(time = x,event = y))},x = survival_master2[,2:4],y = survival_master2[,5:7])
names(surv_objs2)<-names(surv_objs)

reg_output_df<-do.call("rbind",reg_output_l)
reg_output_df<-reg_output_df[-c(5,6),]
out1<-regression_output(coxph(surv_objs$DC ~Site +stage + ecog, data = Cov_Surv,na.action = na.omit))

 out2<-regression_output(coxph(surv_objs$LCRdate ~ ecog + trt + Site,na.action = na.omit, data = Cov_Surv))
 
reg_output_mv<-regression_output(coxph(surv_objs$Living_date ~ stage + Site+age,data=Cov_Surv,na.action = na.omit))

output_csv<-rbind(reg_output_df,reg_output_mv)
output_csv<-round(output_csv,2)
write.csv(output_csv,"DSS1.csv")
#regression_output(coxph(surv_object~treatINT,data=SurvivalHND_trt))
rownames(reg_output_df)<-c("Treatment Interruption(Yes vs No)","Hypopharynx","Larynx","Oral Cavity","Nasopharynx","Stage III/IV","Ecog1","ECOG II/III/IV","Age 80+","CCI 7+")

suv_fits1<-lapply(suv_fits,function(x){names(x)<-c("TI","Site","stage","ecog","age","CCI")}) # rename all the nested lists



```
Below is the code to plot all the Kaplan Meier curves using the "suv_fits" created above



```{r}
plots_listLCR<-lapply(suv_fits1$LCRdate,function(x){ggsurvplot(x,pval=T,xlab="Time(years)",ylab="Locoregional Control",data=Cov_Surv)})

plots_listOS<-lapply(suv_fits1$Living_date,function(x){ggsurvplot(x,pval=T,xlab="Time(years)",ylab="Overall Survival",data=Cov_Surv)})

plots_list_DS<-lapply(suv_fits1$DC,function(x){ggsurvplot(x,pval=T,xlab="Time(years)",ylab = "Disease Specific Survival",data=Cov_Surv)})

c(plots_list_DS,plots_listLCR,plots_listOS)<-lapply(c(plots_list_DS,plots_listOS,plots_list_DS),function(x){names(x)<-c("TI","Site","stage","ecog","age","CCI")})
```

